---
title: "Binary Logistic Regression"
author: "Anna Talken"
date: "2/7/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(GGally)
library(broom)
library(jtools)
```

## Read in the data
```{r}
palmetto <- read_csv(here("data", "palmetto.csv"),
                     col_types = cols(.default = 'c')) %>% 
  
  #convert the following variables to numeric class
  mutate(height = as.numeric(height)) %>% 
  mutate(width = as.numeric(width)) %>% 
  mutate(length = as.numeric(length)) %>% 
  mutate(green_lvs = as.numeric(green_lvs)) %>% 
  
  #select for species, height, length, width, green leaves
    select(species, height, length, width, green_lvs)
```

## Data visualization exploring differences in height, canopy length, canopy width, and green leaves for two species

```{r, fig.cap = "Figure 1. Exploratory scatterplot comparing the maximum canopy hieght and canopy width in Florida Palmettos between two species: Serenoa Repens and Sabal Etonia."}
  ggplot(data = palmetto, aes(x = width, y = height, color = species)) +
  geom_point(na.rm = TRUE) +
  scale_color_manual(values = c("cyan4", "coral")) +
  theme_minimal() +
  labs( title = "Comparison between canopy width and height in Florida Palmettos",
        x = "Width",
        y = "Height")
```

There appears to be a positive correlation between canopy width and height within both species of Florida Palmettos. 


```{r, fig.cap = "Figure 2. A density comparison of the number of green leaves found in each species: Serenoa Repens and Sabal Etonia"}
# Second exploratory graph
ggplot(data = palmetto, aes(x = green_lvs, group = species, fill = species)) +
  geom_density(adjust = 1.5, alpha = 0.5) +
   theme_minimal() +
  labs( title = "Abundance of green leaves found within two species of Florida Palmettos",
        x = "Green Leaves",
        y = "Density")
```
The number of green leaves in Sabal Etonia that makes up the greatest density of total green leaves peaks around 3 to 4 leaves, whereas there is a more spread out density of green leave numbers for Serenoa Repens, with the highest density of green leave numbers at around 6 to 7 leaves. 


```{r, fig.cap = "Figure 3. A comparison between the number of green leaves found and the widest length of the canopy within two species of Florida Palmettos: Serenoa Repens and Sabal Etonia."}
ggplot(data = palmetto, aes(x = green_lvs, y = length, color = species, shape = species)) +
  geom_point() +
  scale_color_brewer() +
  theme_minimal() +
   labs( title = "Comparison of the number of green leaves to canopy length",
        x = "Green Leaves",
        y = "Length")
```
There appears to be a positive correlation between number of green leaves and the widest length of the canopy for both species, though Serenoa Repens appears to have a braoder range of green leave abundance. 


## Binary logistic regression

```{r}
# Turning species into class 'factor'
palmettos <- palmetto %>% 
  mutate(species = as.factor(species))

#Creating a model for binomial logistic regression
palmetto_blr <- glm(species ~ height + length + width + green_lvs,
      data = palmettos,
      family = binomial)

# Get a tidy version of the model using broom
blr_tidy <- broom:: tidy(palmetto_blr)
```


## how successful this model would classify a plant correctly

```{r}
#Converting log odds to the probability of prediting whether the plant is ___ for each observation

blr_fitted <- palmetto_blr %>% 
  broom::augment(type.predict = "response")


ggplot(data = blr_fitted, aes(x = width, y = .fitted)) +
  geom_point(aes(color = species)) + 
  geom_smooth(aes(color = species), se = FALSE) +
  labs(x = "Length",
       y = "Probability of being a")
```

